---
title: "unitroot"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, include = F)
```


Do the github series exhibit sustained lead? If I look at github series A vs github series B, does github series A always stay on top?




```{r}
library(tidyverse)
df <- read.csv("../cleaning/merging-orgs/output/daily_issues.csv")

# male or female codes

mf <- read.csv("../repos/repos.csv") %>% 
  select(owner, sex)

df <- left_join(df, mf)

# just females

df <- df %>% 
  filter(sex == "female")

df %>% 
  group_by(owner, org) %>% 
  count() # only 5 females, 2 for github, 3 for microsoft


githubdf <- df %>% 
  filter(org == "github")

microdf <- df %>% 
  filter(org == "microsoft")

```


run sustained lead analysis on all 5 repos


```{r}
allrepos <- df %>% distinct(repoid) %>% pull(repoid)
allrepos1 <- data.frame(repo1 = c(allrepos))
allrepos2 <- data.frame(repo2 = c(allrepos))
crossrepos <- subset(merge(allrepos1, allrepos2, by = NULL), repo1 <= repo2)
crossrepos <- crossrepos %>% 
  filter(repo1 != repo2)


```



```{r}

savepair <- numeric(nrow(crossrepos))

for(j in 1:nrow(crossrepos)){
 

pair <- crossrepos %>% 
    slice(j)

pairdf <- df %>% 
  filter(repoid %in% c(pair$repo1, pair$repo2))

pairdf %>% 
  group_by(repo) %>% 
  summarize(
    numdays = max(event_at_index)) %>% 
  arrange(numdays) %>% 
  slice(1) %>% pull(numdays) %>% floor() -> series_n

percent <- pairdf %>% 
  filter(event_at_index %in% c(1:series_n)) %>% 
  select(X, event_at_index, value, repoid, repo) %>% 
  group_by(event_at_index) %>% 
  mutate(rk = rank(-value)) %>% 
  filter(repoid == pair$repo1) %>% 
  filter(rk == 1) %>% 
  nrow() / series_n 

  savepair[j] <- percent
  
}




```


Percentages here indicate the number of periods that series x_i was on top. 

```{r}
plotpair <- round(savepair, 1)
ggplot() + geom_histogram(aes(plotpair)) + 
  theme_bw() + 
  labs(x = "Fraction Of Periods With Max Requests", y = "Count")


```


Percents are on the X-axis. X-axis is the fraction of periods that a repo i has the greatest number of requests. The Y-axis shows the number of times a given percentage appears in the data. 1 and 0 occurred a lot, meaning that out of any random pair of request pools, one was likely to remain on top for the entire period. 



Change the image so it looks similar to the theoretical distribution.


```{r}
hm <- data.frame(table(plotpair))
names(hm) <- c('x', 'counts')
totaln <- sum(hm$counts)
hm <- hm %>% 
  mutate(perc = counts / totaln)


hm <- hm %>% 
  mutate(x = as.numeric(as.character(x)))

ggplot(hm, aes(x = x, y = perc)) + 
  geom_bar(stat = "identity", width = 0.1) + 
  theme_bw() + 
  labs(x = "Proportion of n Periods", y = "Probability of Spending n Periods in the Lead") + 
  #theme(axis.text.x = element_blank()) + 
  theme(axis.title.y = element_text(angle = 90)) + 
  scale_x_continuous(breaks = c(0.0, 0.25, 0.50, 0.75, 1.0))



```


```{r}

g <- ggplot(hm, aes(x = x, y = perc)) + 
  geom_bar(stat = "identity", width = 0.1) + 
  theme_bw() + 
  labs(x = "Proportion of n Periods", y = "Probability of Spending n Periods in the Lead") + 
  #theme(axis.text.x = element_blank()) + 
  theme(axis.title.y = element_text(angle = 90)) + 
  scale_x_continuous(breaks = c(0.0, 0.25, 0.50, 0.75, 1.0))

ggsave('allfemale.pdf', g, width = 6, height = 4)

```







run analysis on github females





```{r}
allrepos <- githubdf %>% distinct(repoid) %>% pull(repoid)
allrepos1 <- data.frame(repo1 = c(allrepos))
allrepos2 <- data.frame(repo2 = c(allrepos))
crossrepos <- subset(merge(allrepos1, allrepos2, by = NULL), repo1 <= repo2)
crossrepos <- crossrepos %>% 
  filter(repo1 != repo2)


```



```{r}

savepair <- numeric(nrow(crossrepos))

for(j in 1:nrow(crossrepos)){
 

pair <- crossrepos %>% 
    slice(j)

pairdf <- df %>% 
  filter(repoid %in% c(pair$repo1, pair$repo2))

pairdf %>% 
  group_by(repo) %>% 
  summarize(
    numdays = max(event_at_index)) %>% 
  arrange(numdays) %>% 
  slice(1) %>% pull(numdays) %>% floor() -> series_n

percent <- pairdf %>% 
  filter(event_at_index %in% c(1:series_n)) %>% 
  select(X, event_at_index, value, repoid, repo) %>% 
  group_by(event_at_index) %>% 
  mutate(rk = rank(-value)) %>% 
  filter(repoid == pair$repo1) %>% 
  filter(rk == 1) %>% 
  nrow() / series_n 

  savepair[j] <- percent
  
}




```


Percentages here indicate the number of periods that series x_i was on top. 

```{r}
plotpair <- round(savepair, 1)
ggplot() + geom_histogram(aes(plotpair)) + 
  theme_bw() + 
  labs(x = "Fraction Of Periods With Max Requests", y = "Count")


```


Percents are on the X-axis. X-axis is the fraction of periods that a repo i has the greatest number of requests. The Y-axis shows the number of times a given percentage appears in the data. 1 and 0 occurred a lot, meaning that out of any random pair of request pools, one was likely to remain on top for the entire period. 



Change the image so it looks similar to the theoretical distribution.


```{r}
hm <- data.frame(table(plotpair))
names(hm) <- c('x', 'counts')
totaln <- sum(hm$counts)
hm <- hm %>% 
  mutate(perc = counts / totaln)


hm <- hm %>% 
  mutate(x = as.numeric(as.character(x)))

ggplot(hm, aes(x = x, y = perc)) + 
  geom_bar(stat = "identity", width = 0.1) + 
  theme_bw() + 
  labs(x = "Proportion of n Periods", y = "Probability of Spending n Periods in the Lead") + 
  #theme(axis.text.x = element_blank()) + 
  theme(axis.title.y = element_text(angle = 90)) + 
  scale_x_continuous(breaks = c(0.0, 0.25, 0.50, 0.75, 1.0))



```


```{r}

g <- ggplot(hm, aes(x = x, y = perc)) + 
  geom_bar(stat = "identity", width = 0.1) + 
  theme_bw() + 
  labs(x = "Proportion of n Periods", y = "Probability of Spending n Periods in the Lead") + 
  #theme(axis.text.x = element_blank()) + 
  theme(axis.title.y = element_text(angle = 90)) + 
  scale_x_continuous(breaks = c(0.0, 0.25, 0.50, 0.75, 1.0))

ggsave('githubfemale.pdf', g, width = 6, height = 4)

```


















run analysis on microsoft females





```{r}
allrepos <- microdf %>% distinct(repoid) %>% pull(repoid)
allrepos1 <- data.frame(repo1 = c(allrepos))
allrepos2 <- data.frame(repo2 = c(allrepos))
crossrepos <- subset(merge(allrepos1, allrepos2, by = NULL), repo1 <= repo2)
crossrepos <- crossrepos %>% 
  filter(repo1 != repo2)


```



```{r}

savepair <- numeric(nrow(crossrepos))

for(j in 1:nrow(crossrepos)){
 

pair <- crossrepos %>% 
    slice(j)

pairdf <- df %>% 
  filter(repoid %in% c(pair$repo1, pair$repo2))

pairdf %>% 
  group_by(repo) %>% 
  summarize(
    numdays = max(event_at_index)) %>% 
  arrange(numdays) %>% 
  slice(1) %>% pull(numdays) %>% floor() -> series_n

percent <- pairdf %>% 
  filter(event_at_index %in% c(1:series_n)) %>% 
  select(X, event_at_index, value, repoid, repo) %>% 
  group_by(event_at_index) %>% 
  mutate(rk = rank(-value)) %>% 
  filter(repoid == pair$repo1) %>% 
  filter(rk == 1) %>% 
  nrow() / series_n 

  savepair[j] <- percent
  
}




```


Percentages here indicate the number of periods that series x_i was on top. 

```{r}
plotpair <- round(savepair, 1)
ggplot() + geom_histogram(aes(plotpair)) + 
  theme_bw() + 
  labs(x = "Fraction Of Periods With Max Requests", y = "Count")


```


Percents are on the X-axis. X-axis is the fraction of periods that a repo i has the greatest number of requests. The Y-axis shows the number of times a given percentage appears in the data. 1 and 0 occurred a lot, meaning that out of any random pair of request pools, one was likely to remain on top for the entire period. 



Change the image so it looks similar to the theoretical distribution.


```{r}
hm <- data.frame(table(plotpair))
names(hm) <- c('x', 'counts')
totaln <- sum(hm$counts)
hm <- hm %>% 
  mutate(perc = counts / totaln)


hm <- hm %>% 
  mutate(x = as.numeric(as.character(x)))

ggplot(hm, aes(x = x, y = perc)) + 
  geom_bar(stat = "identity", width = 0.1) + 
  theme_bw() + 
  labs(x = "Proportion of n Periods", y = "Probability of Spending n Periods in the Lead") + 
  #theme(axis.text.x = element_blank()) + 
  theme(axis.title.y = element_text(angle = 90)) + 
  scale_x_continuous(breaks = c(0.0, 0.25, 0.50, 0.75, 1.0)) + 
  xlim(-0.09, 1)



```


```{r}

g <- ggplot(hm, aes(x = x, y = perc)) + 
  geom_bar(stat = "identity", width = 0.1) + 
  theme_bw() + 
  labs(x = "Proportion of n Periods", y = "Probability of Spending n Periods in the Lead") + 
  #theme(axis.text.x = element_blank()) + 
  theme(axis.title.y = element_text(angle = 90)) + 
  scale_x_continuous(breaks = c(0.0, 0.25, 0.50, 0.75, 1.0))+ 
  xlim(-0.09, 1)

ggsave('microsoftfemale.pdf', g, width = 6, height = 4)

```
