---
title: "Time Series Plots"
output:
  rmdformats::material:
    highlight: kate
---

```{r setup, echo=FALSE, cache=FALSE, warning = F, message = F}
library(knitr)
library(rmdformats)
library(tidyverse)
library(ggplot2)
library(data.table)

## Global options
options(max.print="900")
opts_chunk$set(echo=FALSE,
	             cache=FALSE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE,
               fig.width = 10)
opts_knit$set(width=100)
```

# Introduction

Find the github and MSU graduate student data by navigating with the pane on the left. The github data includes 35 time series, each representing the number of issues collected on a repository per day. The MSU student data includes 92 time series, each representing the number of active graduate students in a department per term.

# GitHub Issues


```{r}

load("../github/data/for-analysis-ts/daily_issues.RData")
pt <- data.table(issues_open_daily)
allrepos <- unique(pt$repoidname)

plotissue <- function(rp){
  
  zz <- ggplot(pt[repoidname == rp],
               aes(x = event_at_index, y = value, group = repoidname)) + 
        geom_point(alpha = 0.8) + 
        geom_line(color = "darkblue", alpha = 0.7) + 
        ylim(0, NA) + 
        theme_classic() + 
        labs(x = "Day", y = "Number of Open Issues", title = rp) + 
        theme(axis.text.x = element_blank(),
              axis.ticks.x = element_blank(),
              text = element_text(size = 40)) 
 
  return(zz)
}

```



```{r, fig.width = 25, fig.height = 10}



for(l in 1:length(allrepos)){
  
  gplot <- plotissue(allrepos[l])
  print(gplot)
  
  
}

```



# MSU Students

```{r}

df <- read.csv("../msustudents/data/cleaned/df.csv")
dt <- data.table(df)



all_degrees <- unique(df$degree)

plotit <- function(d){
  
  g <- ggplot(dt[degree == d], aes(x = time, y = total, group = degree_id)) +
         geom_point(alpha = 0.8) + 
         geom_line(color = "darkblue", alpha = 0.7) + 
         labs(x = "Time", y = "Number Graduate Students", title = d) + 
         theme_bw()
  
  return(g)
  
}
```

```{r}
for(i in 1:length(all_degrees)){
  
  plot <- plotit(all_degrees[i])
  print(plot)
  
}
```

# Dickey-Fuller Results

### GitHub Issues


```{r}
library(tidyverse)
library(tseries)
library(plm)
gf <- read.csv("../github/data/for-analysis-ts/daily_issues.csv")


repos <- gf %>% 
  distinct(repo) %>% pull()

repids <- tibble(
  'repo' = repos,
  'repoid' = c(1:length(repos))
)

gf <- left_join(gf, repids)

numdays <- gf %>% 
  group_by(repo) %>% 
  summarize(
    numdays = max(event_at_index))

gf <- left_join(gf, numdays)


runs <- nrow(repids)
store_resultsg <- data.frame(
  "dickeyp" = numeric(runs),
  "kpss" = numeric(runs),
  "repoid" = numeric(runs),
  "dickey" = numeric(runs)
)

for(i in 1:runs){
  
  dt <- gf %>%
    filter(repoid == i)
  
  dtdickey <- plm.data(dt, index = c("repoid", "event_at_index"))

  # not significant = random walk
  dy <- adf.test(dtdickey[, "value"])["p.value"][[1]]
  dt <- adf.test(dtdickey[, "value"])$statistic[[1]]

  # significant = random walk
  kp <- kpss.test(dtdickey[, "value"], null = "Trend")["p.value"][[1]]
  
  
  store_resultsg[[i, "dickeyp"]] <- dy
  store_resultsg[[i, "kpss"]] <- kp
  store_resultsg[[i, "repoid"]] <- i
  store_resultsg[[i, "dickey"]] <- dt
  
  
}



gf$nicedate <- gsub(gf$event_at, pattern = "00:00:00", replacement = "")
library(kableExtra)
store_resultsg <- store_resultsg %>% 
  mutate(DF = ifelse(dickeyp > 0.05, "Yes", "No")) %>% 
  mutate(KP = ifelse(kpss < 0.05, "Yes", "No"))

gf <- left_join(gf, store_resultsg)

gf %>% 
  filter(event_at_index == 0) %>% 
  select(repoid, nicedate, numdays, dickey, dickeyp, DF) %>% 
  mutate(numdays_round = round(numdays, digits = 0)) %>% 
  mutate(dickey = round(dickey, digits = 2)) %>% 
  mutate(dickeyp = round(dickeyp, digits = 2)) %>% 
  select(repoid, nicedate, numdays_round, dickey, dickeyp, DF) %>% 
  mutate(nicedate = as.character(nicedate)) %>% 
  mutate(nicedate = str_trim(nicedate)) %>% 
  mutate(numdays_round = as.character(numdays_round)) %>% 
  mutate(numdays_round = str_trim(numdays_round)) %>% 
  mutate(dickey = as.character(dickey)) %>% 
  mutate(dickey = str_trim(dickey)) %>% 
  mutate(dickeyp = as.character(dickeyp)) %>% 
  mutate(dickeyp = str_trim(dickeyp)) %>% 
  mutate(repoid = as.character(repoid)) %>% 
  mutate(repoid = str_trim(repoid)) %>% 
  rename("Repo ID" = repoid,
         "Start" = nicedate,
         "Length (Days)" = numdays_round,
         "Dickey-Fuller" = dickey,
         "P-Value" = dickeyp,
         "Unit Root" = DF) %>% 
  kable(tabe.attr = "style='width:60%;'") %>% 
  kable_styling() %>% 
  footnote("80% of series contain unit root")


```


### MSU Students


```{r}


library(tidyverse)
library(tseries)
library(plm)
df <- read.csv("../msustudents/data/cleaned/df.csv")

# remove a few series after visual inspection (e.g., they canceled the program)

nouse <- c("College of Medicine-Anatomy",
           "College of Social Science-Psychology-Urban Studies",
           "College of Education-Educational Psychology",
           "College of Natural Science-Entomology")

df <- df %>%
  filter(!degree %in% nouse)


degrees <- unique(df$degree)



runs <- length(degrees)
store_results <- data.frame(
  "dickeyp" = numeric(runs),
  "kpss" = numeric(runs),
  "degree_id" = numeric(runs),
  "timepoints" = numeric(runs),
  "dickey" = numeric(runs)
)

for(i in 1:runs){
  
  dt <- df %>%
    filter(degree == degrees[i])
  
  dtdickey = plm.data(dt, index = c("file", "time"))
  
  dy <- adf.test(dtdickey[, "total"])["p.value"][[1]]
  dstat <- adf.test(dtdickey[, "total"])$statistic[[1]]

  kp <- kpss.test(dtdickey[, "total"])["p.value"][[1]]
  
  store_results[[i, "dickeyp"]] <- dy
  store_results[[i, "kpss"]] <- kp
  store_results[[i, "degree_id"]] <- dt$degree_id[1]
  store_results[[i, "timepoints"]] <- tail(dt$time, 1)
  store_results[[i, "dickey"]] <- dstat
  
  
}



store_results <- store_results %>% 
  mutate(DP = ifelse(dickeyp > 0.05, "Yes", "No")) %>% 
  mutate(KP = ifelse(kpss < 0.05, "Yes", "No"))

df <- left_join(df, store_results)




# describe it in table

library(kableExtra)

df %>% 
  filter(time == 1) %>% 
  mutate(degreecode = c(1:length(degrees))) %>% 
  unite("Start", term, year, sep = "-") %>% 
  select(degreecode, Start, timepoints, dickey, dickeyp, DP) %>% 
  mutate(dickey = round(dickey, digits = 2)) %>% 
  mutate(dickeyp = round(dickeyp, digits = 2)) %>% 
  rename("Degree ID" = degreecode,
         "Start Date" = Start,
         "Length of Series (Semesters)" = timepoints,
         "Dickey-Fuller Statistic" = dickey,
         "P-Value" = dickeyp,
         "Unit Root Present" = DP) %>% 
  kable() %>% 
  kable_styling() %>% 
  footnote("77% of series contain unit root")


```

