---
title: "cleaning"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
knitr::opts_knit$set(root.dir = "../data/working")
```

# Hand exploration to identify col names and relevant rows

1 = graduate major
2 = graduate major identifier?
3 = degree level (e.g., MS, PHD, MFA)
4 = total students across masters and doctoral (so masters would be MS and MFA, etc)
5 = women (of total students)
6 = men (of total students)
7 = NA column
8 = total masters students
9 = total women masters students
10 = total men masters students
11 = NA column
12 = total doctoral students
13 = total women doctoral students
14 = total men doctoral students

Which columns do I need?

1 = graduate major
2 = graduate major identifier (i think that's what this column is...)
12 = total doctoral students

On which row does the actual data begin? row 6

# cleaning

Steps

1) get file names
2) for every file, import and clean
3) save

```{r}
library(tidyverse)
library(readxl)
```


1) get file names

```{r}
knitr::opts_knit$set(root.dir = "../data/working")


files <- Sys.glob("*.xlsx")
files
getwd()
```



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
knitr::opts_knit$set(root.dir = "/tmp")
knitr::opts_knit$set(root.dir = "../data/cleaned")

getwd()
```
