---
title: "unitroot"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, include = F)
```


Load info

```{r}
library(tidyverse)
library(tseries)
library(plm)
df <- read.csv("../clean/3-output/daily_issues.csv")
```


# Descriptives 

Number of repo's assessed:

```{r}
df %>% 
  distinct(repo) %>% nrow()
```


Number of time points per series

```{r}

df %>% 
  group_by(repo) %>% 
  summarize(
    numdays = max(event_at_index))

```

Exclude repos with fewer than 300 days

```{r}
df %>% 
  group_by(repo) %>% 
  summarize(
    numdays = max(event_at_index)) %>% 
  filter(numdays < 500) %>% 
  pull(repo) -> dontuse

df <- df %>% 
  filter(! repo %in% c(dontuse))

```




Start date for each repo

```{r}

repos <- df %>% 
  distinct(repo) %>% pull()

repids <- tibble(
  'repo' = repos,
  'uniqid' = c(1:length(repos))
)

df <- left_join(df, repids)

df %>% 
  filter(event_at_index == 0) %>% 
  select(uniqid, event_at) %>% 
  rename("Repo ID" = uniqid,
         "Start Date" = event_at)
  
```




Put both of those pieces of information into a table

```{r}


numdays <- df %>% 
  group_by(repo) %>% 
  summarize(
    numdays = max(event_at_index))

df <- left_join(df, numdays)

df %>% 
  filter(event_at_index == 0) %>% 
  select(repoid, event_at, numdays) %>% 
  rename("Repo ID" = repoid,
         "Start Date" = event_at,
         "Length of Time Series (Days)" = numdays)
```

# Unit root tests

Practice once

```{r}

df1 <- df %>% 
  filter(repoid == 1)

dfdickey <- plm.data(df1, index = c("repoid", "event_at_index"))

# not significant = random walk
adf.test(dfdickey[, "value"])["p.value"][[1]] # p value
adf.test(dfdickey[, "value"])$statistic[[1]] # test statistic


# significant = random walk
kpss.test(dfdickey[, "value"], null = "Trend")["p.value"][[1]]


```

Loop over each time series

```{r}

runs <- nrow(repids)
store_results <- data.frame(
  "dickeyp" = numeric(runs),
  "kpss" = numeric(runs),
  "repoid" = numeric(runs),
  "dickey" = numeric(runs)
)

for(i in 1:runs){
  
  dt <- df %>%
    filter(uniqid == i)
  
  dtdickey <- plm.data(dt, index = c("repoid", "event_at_index"))

  # not significant = random walk
  dy <- adf.test(dtdickey[, "value"])["p.value"][[1]]
  dt <- adf.test(dtdickey[, "value"])$statistic[[1]]

  # significant = random walk
  kp <- kpss.test(dtdickey[, "value"], null = "Trend")["p.value"][[1]]
  
  
  store_results[[i, "dickeyp"]] <- dy
  store_results[[i, "kpss"]] <- kp
  store_results[[i, "repoid"]] <- i
  store_results[[i, "dickey"]] <- dt
  
  
}

store_results %>% 
  filter(dickeyp > 0.05) %>% 
  count() / nrow(store_results)

store_results %>% 
  filter(kpss < 0.05) %>% 
  count() / nrow(store_results)


(store_results %>%
  filter(dickeyp > 0.05, kpss < 0.05) %>%
  count()) / nrow(store_results)
```


Place results into a table

```{r, eval = F}

df$nicedate <- gsub(df$event_at, pattern = "00:00:00", replacement = "")
library(kableExtra)
store_results <- store_results %>% 
  mutate(DF = ifelse(dickeyp > 0.05, "Yes", "No")) %>% 
  mutate(KP = ifelse(kpss < 0.05, "Yes", "No"))

df <- left_join(df, store_results)

df %>% 
  filter(event_at_index == 0) %>% 
  select(uniqid, nicedate, numdays, dickey, dickeyp, DF) %>% 
  mutate(numdays_round = round(numdays, digits = 0)) %>% 
  mutate(dickey = round(dickey, digits = 2)) %>% 
  mutate(dickeyp = round(dickeyp, digits = 2)) %>% 
  select(uniqid, nicedate, numdays_round, dickey, dickeyp, DF) %>% 
  mutate(nicedate = as.character(nicedate)) %>% 
  mutate(nicedate = str_trim(nicedate)) %>% 
  mutate(numdays_round = as.character(numdays_round)) %>% 
  mutate(numdays_round = str_trim(numdays_round)) %>% 
  mutate(dickey = as.character(dickey)) %>% 
  mutate(dickey = str_trim(dickey)) %>% 
  mutate(dickeyp = as.character(dickeyp)) %>% 
  mutate(dickeyp = str_trim(dickeyp)) %>% 
  mutate(uniqid = as.character(uniqid)) %>% 
  mutate(uniqid = str_trim(uniqid)) %>% 
  rename("Repo ID" = uniqid,
         "Start" = nicedate,
         "Length (Days)" = numdays_round,
         "Dickey-Fuller" = dickey,
         "P-Value" = dickeyp,
         "Unit Root" = DF) %>% 
  kable(tabe.attr = "style='width:60%;'") %>% 
  kable_styling() #%>% 
  #footnote("80% of series contain unit root")

```


```{r, include = T}
library(flextable)
df$nicedate <- gsub(df$event_at, pattern = "00:00:00", replacement = "")
library(kableExtra)
store_results <- store_results %>% 
  mutate(DF = ifelse(dickeyp > 0.05, "Yes", "No")) %>% 
  mutate(KP = ifelse(kpss < 0.05, "Yes", "No"))

df <- left_join(df, store_results)


fitdf <- df %>% 
  filter(event_at_index == 0) %>% 
  select(uniqid, nicedate, numdays, dickey, dickeyp, DF) %>% 
  mutate(numdays_round = round(numdays, digits = 0)) %>% 
  mutate(dickey = round(dickey, digits = 2)) %>% 
  mutate(dickeyp = round(dickeyp, digits = 2)) %>% 
  select(uniqid, nicedate, numdays_round, dickey, dickeyp, DF) %>% 
  rename("Repo ID" = uniqid,
         "Start Date" = nicedate,
         "Length (Days)" = numdays_round,
         "Dickey-Fuller" = dickey,
         "P-Value" = dickeyp,
         "Unit Root" = DF) 

fitdf <- flextable(fitdf)
fitdf <- autofit(fitdf)
fitdf <- fontsize(fitdf, size = 9)
fitdf



```






# Sustained lead analysis



Do the github series exhibit sustained lead? If I look at github series A vs github series B, does github series A always stay on top?




```{r}
library(tidyverse)
df <- read.csv("../clean/3-output/daily_issues.csv")
```


```{r}
allrepos <- df %>% distinct(repoid) %>% pull(repoid)
allrepos1 <- data.frame(repo1 = c(allrepos))
allrepos2 <- data.frame(repo2 = c(allrepos))
crossrepos <- subset(merge(allrepos1, allrepos2, by = NULL), repo1 <= repo2)
crossrepos <- crossrepos %>% 
  filter(repo1 != repo2)


```



```{r}

savepair <- numeric(nrow(crossrepos))

for(j in 1:nrow(crossrepos)){
 

pair <- crossrepos %>% 
    slice(j)

pairdf <- df %>% 
  filter(repoid %in% c(pair$repo1, pair$repo2))

pairdf %>% 
  group_by(repo) %>% 
  summarize(
    numdays = max(event_at_index)) %>% 
  arrange(numdays) %>% 
  slice(1) %>% pull(numdays) %>% floor() -> series_n

percent <- pairdf %>% 
  filter(event_at_index %in% c(1:series_n)) %>% 
  select(X, event_at_index, value, repoid, repo) %>% 
  group_by(event_at_index) %>% 
  mutate(rk = rank(-value)) %>% 
  filter(repoid == pair$repo1) %>% 
  filter(rk == 1) %>% 
  nrow() / series_n 

  savepair[j] <- percent
  
}




```


Percentages here indicate the number of periods that series x_i was on top. 

```{r}
plotpair <- round(savepair, 1)
ggplot() + geom_histogram(aes(plotpair)) + 
  theme_bw() + 
  labs(x = "Fraction Of Periods With Max Requests", y = "Count")
```


Percents are on the X-axis. X-axis is the fraction of periods that a repo i has the greatest number of requests. The Y-axis shows the number of times a given percentage appears in the data. 1 and 0 occurred a lot, meaning that out of any random pair of request pools, one was likely to remain on top for the entire period. 



Change the image so it looks similar to the theoretical distribution.


```{r}
hm <- data.frame(
  'freqs' = c(plotpair)
)
hm <- hm %>% 
  count(freqs) %>% 
  mutate(perc = n / nrow(hm))

ggplot(hm, aes(x = freqs, y = perc)) + 
  geom_bar(stat = "identity") + 
  theme_bw() + 
  labs(x = "Proportion of n Periods", y = "Probability of Spending n Periods in the Lead") + 
  #theme(axis.text.x = element_blank()) + 
  theme(axis.title.y = element_text(angle = 0))



```


```{r}

ggplot(hm, aes(x = freqs, y = perc)) + 
  geom_bar(stat = "identity") + 
  theme_bw() + 
  labs(x = "Proportion of n Periods", y = "Probability of Spending n Periods in the Lead")



gplot <- ggplot(hm, aes(x = freqs, y = perc)) + 
  geom_bar(stat = "identity") + 
  theme_bw() + 
  labs(x = "Proportion of n Periods", y = "Probability of Spending n Periods in the Lead") + 
  theme(text = element_text(size = 14))


ggsave('use.pdf', gplot, width = 10, height = 8)
```


```{r}

ggplot(hm, aes(x = freqs, y = perc)) + 
  #geom_bar(stat = "identity", position = "dodge", alpha = 0.3) +
  geom_density(stat = "identity", alpha = 0.5) + 
  theme_bw() + 
  labs(x = "Proportion of n Periods", y = "Probability of Spending n Periods in the Lead",
       fill = "") 
```




